Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-11-18 paper/paper.tex
Fatter nodes

We perform our experiments on systems with dual Intel Xeon E5-2640 v2 processors and 64GBytes RAM,
running Ubuntu 14.04, with GCC 5.3.0 as the compiler. Each machine has a total of sixteen cores, and
hyper-threading is enabled, so we run experiments with 32 threads except where otherwise noted, but
we do not expect speedups of 32 even in the ideal case.  We run all our experiments with a one
hundred second timeout for each instance. All of our sequential runtimes are from optimised
implementations which were not designed with parallelism in mind---that is, speedups from
parallelism are genuine improvements over the state of the art.

@@

    \caption{In the first two plots, per-instance speedups, using the $k{\downarrow}$ algorithm. The
    $x$-axis is sequential performance and the $y$-axis is 32 threaded performance. Next,
    scalability and reproducibility, and finally, aggregate speedups for both
    families.}\label{figure:kdownscatters}
\end{figure}

>>>>

We perform our experiments on systems with dual Intel Xeon E5-2697A v4 processors and 512GBytes RAM,
running Ubuntu 17.04, with GCC 6.3.0 as the compiler. Each machine has a total of thirty two cores.
We run all our experiments with a one thousand second timeout for each instance. All of our
sequential runtimes are from optimised implementations which were not designed with parallelism in
mind---that is, speedups from parallelism are genuine improvements over the state of the art.

@@

    \caption{In the first two plots, per-instance speedups, using the $k{\downarrow}$ algorithm. The
    $x$-axis is sequential performance and the $y$-axis is 32 threaded performance. Next,
    scalability and reproducibility, and finally, aggregate speedups for both
    families (shown using both types of hardware).}\label{figure:kdownscatters}
\end{figure}
